Traffic Aware Resource Allocation Schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} Systems

### 2015-11-27 Response/Response 3/response-3.tex

\begin{enumerate}

\item \reviewF{When discussing the convergence of the \ac{SCA} algorithm (Appendix A-C), the authors claim that the \ac{SCA} algorithm converges because the objective function is strictly decreasing and the minimizer in each iteration is unique. However, this is in general not enough to guarantee the convergence of the whole sequence. Instead, one can only claim that every limit point of the whole sequence is a stationary point, or globally optimal solution if the problem is convex. As an example, simply consider the gradient projection algorithm, where each subproblem is strongly convex and the objective function  is strictly decreasing but the whole sequence may not converge. The authors are referred to Bertsekas'  book: Nonlinear Programming.}

\vspace{1eM}
\underline{\textbf{Response:}} We thank the reviewer for pointing out that the sequence of iterates generated by the \ac{SCA} algorithm in each \ac{AO} step need not be convergent. Based on the reviewer's reference to the gradient projection algorithm in Nonlinear Programming textbook, we have realized that our earlier convergence proof is not mathematically rigorous. We apologize for our emphasis on the convergence of iterates in our previous manuscript. As suggested by the reviewer, stationarity of limit points of the whole sequence of iterates is now addressed in Appendix A-D by using the following statements: 
\begin{itemize}
	\item The sequence of iterates generated by the algorithm is bounded, therefore, we can claim that there exist at least one subsequence of original sequence that converges to a limit point of original sequence.
	\item Using a convergent subsequence of original sequence of iterates, we then discuss that every limit point is a stationary point of nonconvex problem in Appendix A-D.
\end{itemize}

@@

We have made changes in Appendices A-C and A-D to address the concerns raised by the reviewer.

\vspace{1eM}	
\item \reviewF{Even under the assumption that the inner loop SCA converges, there are doubts with respect to the convergence of the alternating optimization algorithm described by (54). The authors cite [27] to justify convergence, but it is not straightforward to claim that the algorithmic model considered in this manuscript is the same as in [27]. More specifically, let us consider the variable \eqn{x} (so it is consistent with the authors' notation in Appendix A-D). In the algorithmic model of [27], at iteration \eqn{t+1}, all elements of \eqn{\mbf{x}} are updated simultaneously, based on \eqn{\sol{t}}. But in the authors' model, the update of \eqn{\mbf{x}} is performed in two phases: in the first phase, only the elements of \eqn{\mbf{m}} and \eqn{\mbf{\gamma}} in \eqn{\mbf{x}} are updated based on \eqn{\sol{t}}. In the second phase, the remaining elements of \eqn{\mbf{x}} are updated, i.e. \eqn{\mbf{w}} and \eqn{\mbf{\gamma}}, based on both \eqn{\sol{t}} and the elements that have been updated in the first phase. This is not a trivial difference and thus the direct application of the conclusion from [27] in the current context cannot be taken for granted. Due to the open concerns after several revision rounds, it is recommended to reject the paper.}

\vspace{1eM}
\underline{\textbf{Response:}} We understand the reviewer's concern on using reference [R1] to our problem involving both \ac{SCA} and \ac{AO} updates. In each iteration, the proposed method solves only a subset of optimization variables by keeping the others fixed. Therefore, we cannot use reference [R1] directly as suggested by the reviewer, and we have now completely revised the argumentation as detailed above. Even though we have revised our convergence proof based on a convergent subsequence without referring to [R1], nevertheless, we clarify our usage of [R1] in our previous manuscript for the convergence of iterates:

\begin{itemize}
	\item We refer to [R2] for a similar usage of reference [R1] while discussing the convergence of \ac{AO} method used in designing tight frames by solving matrix nearness problem. Reference [R1] is used to discuss the convergence of iterates generated by the \ac{AO} method in [R2] by referring \ac{AO} update as a composition of two sub-algorithms, wherein each sub-algorithm updates only a subset of optimization variables. It has been discussed comprehensively in [R2, Appendices I and II]. In particular, the discussion on referring \ac{AO} as two sub-algorithms is presented in [R2, Appendix I-F].
	\item However, we apologize for the incomplete usage of [R1, Theorem 3.1] in our previous manuscript to claim the convergence of beamformer iterates. In [R1, Theorem. 3.1], it has been shown that if the strict monotonicity of the objective sequence is ensured and the iterates are bounded, then \textit{either the sequence of iterates converges or the accumulation points of \eqn{\{\sol{t}\}} is a continuum}.
	\item Therefore, our previous statement claiming guaranteed convergence of iterates is not correct, as pointed out by the reviewer. 
	\item A similar approach of restricting the solution set with a proximal operator to ensure strict monotonicity of the objective sequence is presented in [R1, Section 4] under restrictive mapping title. Therefore, even if we use the discussions from reference [R1], we can only claim that the sequence of iterates \eqn{\{\sol{t}\}} converges to a continuum of accumulation points, and every limit point is a stationary point.
\end{itemize}

We have revised Appendix A-D titled \textit{"Stationarity of Limit Points"} to address the convergence of the sequence of iterates. We have revised our statement as every limit point of the sequence of iterates generated by the centralized algorithm is a stationary point.

### 2015-11-27 Response/Response 3/reviewer_response.tex

\title{Reviewers Comments \& Authors Replies}

\date{}
\maketitle

\begin{tabular}{p{1.25in}p{4.25in}}
	\textbf{Manuscript No.} & Paper T-SP-18051-2014, submitted to \emph{``IEEE Transactions on Signal Processing"} \\ \\
	\textbf{Title} & ``Traffic Aware Resource Allocation Schemes for Multi-Cell MIMO-OFDM Systems" \\ \\
	\textbf{Authors} & Ganesh Venkatraman, Antti T\"{o}lli, Markku Juntti, and Le-Nam Tran
\end{tabular}

\vspace{0.35in}
The authors are grateful to the associate editor for giving us an additional opportunity to revise and correct our convergence analysis. In this regard, we would like to give a special thank to Reviewer 3 who pointed out the issues with our convergence analysis of the proposed solutions. In this revision, we have mainly focused on providing a more mathematically rigorous  proof of the convergence analysis of the proposed iterative algorithms.
%\input{additions}
Towards this end the following changes have been made to the revised manuscript.
\begin{enumerate}
	\item We have restated the convergence results of the centralized algorithms in this revision, claiming that any accumulation point (i.e., limit point) is a stationary point. The proof is essentially based on the convergence of a subsequence of iterates. We have rewritten Appendix A-D according to these changes. In particular, to discuss the convergence of the sequence of iterates generated by the centralized method, we use a unified superscript index \eqn{t} to refer to the step index of both \ac{AO} and \ac{SCA} procedures (\textit{i.e.}, index \eqn{t} denotes \ac{SCA} and \ac{AO} update step (\eqn{k,i})). Then, by using index \eqn{t}, we denote iterate \eqn{\ma^t} as a vector formed by stacking the minimizer of problem (48) at iteration \eqn{t} as \eqn{\mat{t} = \mbf{z}^{(i)}_k}, and let \eqn{\{\mat{t}\}} be the sequence formed by collecting the minimizers of problem (48) from each iteration. With these notations, we have revised our convergence discussions in Appendices A-C and A-D.		
	\item We have updated the convergence of distributed algorithms in a similar way.
\end{enumerate}

### 2015-11-27 Report/convergence_centralized.tex
submitted

The following conditions are required to show the convergence of Algorithm \ref{algo-1}, which is used to solve problems \eqref{eqn-6} and \eqref{eqn-mse-1} in an iterative manner.
\begin{itemize}
\item[(a)] Uniqueness of the minimizer in each step
\item[(b)] Objective function should be bounded below
\item[(c)] Feasible set should be compact
\item[(d)] Sequence of objective values should be strictly decreasing
\end{itemize}
Note that the uniqueness condition in (a) is required to ensure strict monotonicity in the objective sequence. Upon satisfying conditions (a)-(d), we can show that the objective sequence generated by the centralized approach in Algorithm \ref{algo-1} converges, by using \cite[Th. 3.14]{rudin1964principles}. Then, by following the discussions in \cite{marks1978technical,lanckriet2009convergence,scutari_1}, we can claim that \reviewF{every limit point of the sequence of iterates generated by the iterative method is a stationary point of original nonconvex formulations in \eqref{eqn-6} and \eqref{eqn-mse-1}}.

@@

We use the following notations to discuss the convergence of Algorithm \ref{algo-1}. Since it involves two nested loops, \textit{i.e.}, one for \ac{SCA} and another for \ac{AO}, we denote the \ac{AO} step by a superscript \me{(i)} and the \ac{SCA} iteration by a subscript \me{k}. Let \me{\mx}, \me{\my}, and \me{\mz} be the vector stacking all transmit precoders, receive beamformers, and other optimization variables used in \eqref{eqn-6} and \eqref{eqn-mse-1}, respectively. Now, let us consider \ac{AO} step \eqn{i} with fixed \eqn{\my}. The solution obtained in the \eqn{\ith{k}} \ac{SCA} step is given by \eqn{\mx=\iter{\mx}{k}{i}} and \eqn{\mz=\iter{\mz}{k}{i}}. As \eqn{k \to \infty}, objective sequence converges, and the respective solution is denoted by \me{\iter{\mx}{\lpointx}{i}} and \me{\iter{\mz}{\lpointx|\my}{i}}. Similarly, while alternating the optimization variables for fixed \eqn{\mx}, as \eqn{k \to \infty}, the solution obtained is represented as \me{\my = \iter{\my}{\lpointx}{i}} and \me{\mz = \iter{\mz}{\lpointx|\mx}{i}}. In the following, we will show that the conditions in (a)-(d) are satisfied by Algorithm \ref{algo-1}.

@@

To ensure the uniqueness of transmit and receive beamformers in each iteration, the objective function of subproblems \eqref{eqn-9} and \eqref{eqn-mse-2} is regularized by a strongly convex function in each \ac{SCA} iteration \eqn{k} and \ac{AO} update step \eqn{i} as 
\begin{IEEEeqnarray}{rCl} \neqsub
\hat{f}(\mbf{z}) &=& \| \tilde{\mbf{v}} \|_q \eqsub \label{orig_obj} \\ 
f(\mbf{z}) &=& \hat{f}(\mbf{z}) + {\tau}_k^{(i)} \, \| \mbf{z} - \mbf{z}^{(i)}_{k} \|^2_2 \eqsub \label{mod_obj} 
\end{IEEEeqnarray}
where vector \eqn{\mbf{z}} is formed by stacking all optimization variables that can be either \eqn{[\mx,\iter{\my}{\lpoint}{i-1},\mz]} or \eqn{[\iter{\mx}{\lpoint}{i},\my,\mz]} depending on the fixed variables. Moreover, \eqn{\mbf{z}^{(i)}_{k} \triangleq [\mx_{k}^{(i)},\iter{\my}{\lpoint}{i-1},\mz_{k}^{(i)}]} be a stacked vector of solution obtained at the \eqn{\ith{(k-1)}} \ac{SCA} step in \ac{AO} iteration \eqn{i}. The positive constant \me{{\tau}_{k}^{(i)} > 0} ensures strong convexity of \eqn{f(\mbf{z})} in each step \cite[Sec. 3.4.3]{bertsekas1989parallel}. Thus, due to strong convexity in \eqn{f(\mbf{z})}, uniqueness of the minimizer is ensured in each \ac{SCA} step \cite{yang_yang,scutari-1}.

@@

Since the norm function present in the objective satisfies \me{\|\tilde{\mbf{v}}\|_q \geq 0} for all \eqn{q} used in \eqn{\ell_q} norm, it is bounded from below. Moreover, due to the compactness of the feasible set, it is bounded from above as well. In addition, the objective function satisfies Lipschitz continuity, since the feasible set is compact.

@@

where \eqn{c > 0} be the constant of strong convexity, defined as \eqn{c \triangleq \min_{k} \{{\tau}_{k}^{(i)}\}}, and \eqn{\iter{\mbf{z}}{k+1}{i}} is the solution. Therefore, by using \eqref{strict_monotonicity} and \eqn{\iter{\mbf{z}}{k}{i} \in \iter{\mc{X}}{k}{i}}, we can show that \eqn{f(\iter{\mbf{z}}{k}{i}) > f(\iter{\mbf{z}}{k+1}{i})} holds strictly in each \ac{SCA} step unless \eqn{\mbf{z}_{k}^{(i)} \to \mbf{z}_{\lpoint}^{(i)}} as \eqn{k \to \infty}. Now, by utilizing the facts that (i) \eqn{\{f(\mbf{z}^{(i)}_k)\}} is monotonic, and (ii) the uniqueness of the minimizer (see \eqref{strict_monotonicity}), strict monotonicity of \eqn{\{f(\mbf{z}^{(i)}_k)\}} is ensured in each \ac{SCA} step \cite{scutari2010convex}. \reviewF{Additionally, by using the fact that \eqn{\{f(\mbf{z}^{(i)}_k)\}} is bounded, we can ensure that \eqn{\{f(\mbf{z}_k^{(i)})\}} converges as \eqn{k \to \infty} in \ac{AO} step \eqn{i}. Let \eqn{\mbf{z}_{\lpoint}^{(i)} \triangleq \{\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}\}} denote a stacked vector of the minimizer obtained upon the objective convergence in \ac{AO} iteration \eqn{{i}}.}

@@

\subsection{Stationarity of Limit Points} \label{c-b}
\reviewF{We now discuss the convergence properties of sequence of iterates. For convenience, let us consider a unified superscript \eqn{t} to refer to the index of both \ac{SCA} and \ac{AO} procedures (\textit{i.e.}, index \eqn{t} denotes \ac{SCA} step \eqn{k} and \ac{AO} step \eqn{i}). Then, we denote iterate \eqn{\ma^t} as a vector formed by stacking minimizer obtained by solving \eqref{con-m} at iteration \eqn{t} as \eqn{\mat{t} = \mbf{z}^{(i)}_k}, and \eqn{\{\mat{t}\}} be the sequence formed by collecting minimizers from each iteration.

Note that the objective sequence \eqn{\{f(\ma^t)\}} is bounded and nonincreasing (see Appendices \ref{b_obj} and \ref{mcity}). Therefore, by using \cite[Prop. A.3]{bertsekas1999nonlinear}, we can ensure the convergence of \eqn{\{f(\ma^t)\}}. Unfortunately, such a claim cannot be made on the convergence of sequence of iterates \eqn{\{\ma^t\}}. However, due to compactness of the feasible set, the sequence of iterates \eqn{\{\ma^t\} \subset \mc{F}} is bounded, and therefore the sequence \eqn{\{\mat{t}\}} has at least one limit such that there exists a subsequence of \eqn{\{\ma^t\}} that converges to it, by following \cite[Prop. A.5]{bertsekas1999nonlinear}.

@@

Let us prove the stationarity of \eqn{\bar{\ma}} by contradiction. Assume that \eqn{\bar{\ma}} is not a stationary point, then there exist some other point \eqn{\ma^\prime \in \{\ma^t\}}, such that \eqn{\nabla f (\bar{\ma})^\tran (\ma^\prime - \bar{\ma}) < 0} and \eqn{f(\bar{\ma}) > f(\ma^\prime)}. Since \eqn{\ma^\prime} is a point in \eqn{\{\ma^t\}}, there exist a subsequence that converges to \eqn{\ma^\prime}, for which \eqn{\ma^\prime} is a limit point. However, by using \eqref{limpoint}, we have \eqn{f(\bar{\ma}) = f(\ma^\prime)} for all limit points of \eqn{\{\ma^t\}}, which is a contradiction to our initial assumption.

Now, by using strict monotonicity of \eqn{\{f(\ma^{t_j})\}}, it follows that as \eqn{j \to \infty}, \eqn{\ma^{t_j} \to \bar{\ma}} and \eqn{f(\ma^{t_{j}}) - f(\ma^{t_{j+1}}) \to 0}. Moreover, since \eqn{\bar{\ma}} is the solution of \eqref{con-m}, it satisfies \eqref{strict_monotonicity} over convex subset \eqn{\mc{Q}}, which can either be \eqn{\iter{\mc{X}}{k}{i}} or \eqn{\iter{\mc{Y}}{k}{i}} as \eqn{k \to \infty, i \to \infty}. Using the above statements, we can show that \eqn{\bar{\ma}} satisfies the optimality condition  \cite[Prop. 2.1.2]{bertsekas1999nonlinear} as 
\begin{equation} \label{seq_mon1}
\nabla f (\bar{\ma})^\tran (\ma - \bar{\ma}) \geq 0, \; \fall \ma \in \mc{Q} \subset \mc{F} \eqsub.
\end{equation}
Thus, \eqn{\bar{\ma}} is a stationary point, and by using \eqref{limpoint}, we can show that every limit point of \eqn{\{\ma^t\}} is a stationary point of \eqref{con-m}.

@@

Now to prove that \eqn{\bar{\ma}} is also a stationary point of original problem \eqref{con}, we show the equivalence between the gradients of \eqref{con-m} and \eqref{con} at \eqn{\bar{\ma}}. In order to ensure that \eqn{\bar{\ma}} is a \ac{KKT} point of \eqref{con}, it must satisfy the gradient condition of \eqref{con} as
\begin{equation} \label{kkt_expr}
\textstyle	\nabla \hat{f}(\bar{\ma}) + \mu_0 \big [ \nabla h(\bar{\ma}) - \nabla {g}_0(\bar{\ma}) \big ] + \sum_{i=1}^2 \mu_i \nabla g_i(\bar{\ma}) = 0
\end{equation}
for some Lagrange multipliers \eqn{\mu_i \geq 0} and feasible as \eqn{\bar{\ma} \in \mc{F}}.

Using \eqref{con-sub-set}, we have \eqn{\mc{X}_{k}^{(i)} \subset \mc{F}} and \eqn{\mc{Y}_{k}^{(i)} \subset \mc{F}}, therefore, \eqn{\bar{\ma}} is a feasible point for \eqref{con}. Moreover, the interiors of \eqn{\mc{X}_{k}^{(i)}} and \eqn{\mc{Y}_{k}^{(i)}} are non-empty, therefore, Slater's constraint qualification holds for \eqref{con-m}. Since \eqn{\bar{\ma}} is the solution for \eqref{con-m} as \eqn{k \to \infty,i \to \infty}, there exist Lagrange multipliers \eqn{\mu_i \geq 0} that  satisfies
\begin{equation} \label{kkt_mod_expr}
\textstyle \nabla f(\bar{\ma}) + \mu_0 \big [ \nabla h(\bar{\ma}) - \nabla\hat{g}_0(\bar{\ma};\bar{\ma}) \big ] + \sum_{i=1}^2 \mu_i \nabla g_i(\bar{\ma}) = 0.
\end{equation}

The relation between \eqref{kkt_expr} and \eqref{kkt_mod_expr} is evident by using following facts: (i) The quadratic term in \eqref{mod_obj} \eqn{\|\ma^{t_{j+1}} - \ma^{t_j}\|^2 \to 0}  as \eqn{j \to \infty, \ma^{t_j} \to \bar{\ma}}, since we assume that \eqn{\bar{\ma}} is the limit point of a convergent subsequence \eqn{\{\ma^{t_j}\}}. Therefore, the gradient evaluated at \eqn{\bar{\ma}} satisfies \eqn{\nabla {f}(\bar{\ma}) = \nabla \hat{f}(\bar{\ma})}. (ii) Additionally, by using the continuity of function \eqn{g_o} and \eqref{con-relax}, equivalence between the gradient of \eqref{con-dc} and \eqref{con-dc-m} is obtained as \eqn{\ma^{t_j} \to \bar{\ma}}
\begin{equation} \label{rhs_equiv}
\nabla h(\bar{\ma}) - \nabla \hat{g}_o(\bar{\ma};\bar{\ma}) = \nabla h(\bar{\ma}) - \nabla g_o(\bar{\ma}).
\end{equation}
Now, by applying the relation \eqref{rhs_equiv} and \eqn{\nabla {f}(\bar{\ma}) = \nabla \hat{f}(\bar{\ma})} in \eqref{kkt_mod_expr}, we can show that limit point \eqn{\bar{\ma}} satisfies \eqref{kkt_expr}. Finally, by using above discussions for every limit point, and by using \cite[Thm. 2]{scutari_1} and \cite[Prop. 3.2]{amir}, we can show that every limit point of sequence of iterates \eqn{\{\ma^t\}} is a stationary point of \eqref{con}.}
%using \cite[Thms. 2 and 11]{scutari_1} and \cite[Prop. 3.2]{amir}, we can show that every limit point of sequence of iterates \eqn{\{\ma^t\}} generated by the iterative algorithm is a stationary point of problem \eqref{con}.}

>>>>

The following conditions are required to show the convergence of Algorithm \ref{algo-1}, which is used to solve problems \eqref{eqn-6} and \eqref{eqn-mse-1} in an iterative manner.
\begin{itemize}
\item[(a)] Uniqueness of the minimizer in each step
\item[(b)] Objective function should be bounded below
\item[(c)] Feasible set should be compact
\item[(d)] Sequence of objective values should be strictly decreasing
\end{itemize}
The uniqueness condition in (a) is required to ensure strict monotonicity in the objective sequence. Therefore, upon satisfying the conditions (a)-(d), we can show that the objective sequence generated by Algorithm \ref{algo-1} converges, by using \cite[Th. 3.14]{rudin1964principles}. Then, by following the discussions in \cite{marks1978technical,lanckriet2009convergence,scutari_1}, we can show that \reviewF{every limit point of sequence of iterates is a stationary point of nonconvex problems in \eqref{eqn-6} and \eqref{eqn-mse-1}}.

@@

We use the following notations to discuss the convergence of Algorithm \ref{algo-1}. Since it involves two nested loops, \textit{i.e.}, one for \ac{SCA} and another for \ac{AO}, we denote the \ac{AO} step by a superscript \me{(i)} and the \ac{SCA} iteration by a subscript \me{k}. Let \me{\mx}, \me{\my}, and \me{\mz} be the vector stacking all transmit precoders, receive beamformers, and other optimization variables used in \eqref{eqn-6} and \eqref{eqn-mse-1}, respectively. Now, let us consider \ac{AO} step \eqn{i} with fixed \eqn{\my}. The solution obtained in the \eqn{\ith{k}} \ac{SCA} step is given by \eqn{\mx=\iter{\mx}{k}{i}} and \eqn{\mz=\iter{\mz}{k}{i}}. As \eqn{k \to \infty}, objective sequence converges, and the respective solution is denoted by \me{\iter{\mx}{\lpointx}{i}} and \me{\iter{\mz}{\lpointx|\my}{i}}. Similarly, while alternating the optimization variables for fixed \eqn{\mx}, as \eqn{k \to \infty}, the solution obtained is represented as \me{\my = \iter{\my}{\lpointx}{i}} and \me{\mz = \iter{\mz}{\lpointx|\mx}{i}}. In the following discussion we will show that the conditions listed in (a)-(d) are satisfied by Algorithm \ref{algo-1} using the above notations.

@@

To ensure the uniqueness of transmit and receive beamformers in each iteration, the objective function of subproblems \eqref{eqn-9} and \eqref{eqn-mse-2} is regularized by a strongly convex function in each \ac{SCA} iteration \eqn{k} and \ac{AO} update step \eqn{i} as 
\begin{IEEEeqnarray}{rCl} \neqsub
\hat{f}(\mbf{z}) &=& \| \tilde{\mbf{v}} \|_q \eqsub \label{orig_obj} \\ 
f(\mbf{z}) &=& \hat{f}(\mbf{z}) + {\tau}_k^{(i)} \, \| \mbf{z} - \mbf{z}^{(i)}_{k} \|^2_2 \eqsub \label{mod_obj} 
\end{IEEEeqnarray}
where \eqn{\mbf{z}} is a vector formed by stacking all the optimization variables, \textit{i.e.}, \eqn{[\mx,\iter{\my}{\lpoint}{i-1},\mz]} or \eqn{[\iter{\mx}{\lpoint}{i},\my,\mz]} depending on the variables being optimized, and \eqn{\mbf{z}^{(i)}_{k} \triangleq [\mx_{k}^{(i)},\iter{\my}{\lpoint}{i-1},\mz_{k}^{(i)}]} is a vector formed by stacking the solution obtained from \ac{SCA} step \eqn{k-1} and \ac{AO} iteration \eqn{i}, respectively. The positive constant \me{{\tau}_{k}^{(i)} > 0} ensures strong convexity of \eqn{f(\mbf{z})} in each step \cite[Sec. 3.4.3]{bertsekas1989parallel}. Thus, due to strong convexity in \eqn{f(\mbf{z})}, uniqueness of the minimizer is ensured in each iteration \cite{yang_yang,scutari-1}.

@@

Note that the norm function present in the objective satisfies \me{\|\tilde{\mbf{v}}\|_q \geq 0} for all exponents \eqn{q} used in \eqn{\ell_q} norm, therefore, it is bounded from below. Moreover, due to the compactness of the feasible set, it is bounded from above as well.

@@

where \eqn{c > 0} be the constant of strong convexity, defined as \eqn{c \triangleq \min_{k} \{{\tau}_{k}^{(i)}\}}, and \eqn{\iter{\mbf{z}}{k+1}{i}} is the solution. Therefore, by using \eqref{strict_monotonicity} and \eqn{\iter{\mbf{z}}{k}{i} \in \iter{\mc{X}}{k}{i}}, we can show that \eqn{f(\iter{\mbf{z}}{k}{i}) > f(\iter{\mbf{z}}{k+1}{i})} holds strictly in each \ac{SCA} step unless \eqn{\mbf{z}_{k}^{(i)} \to \mbf{z}_{\lpoint}^{(i)}} as \eqn{k \to \infty}. Now, by utilizing the facts that (i) \eqn{\{f(\mbf{z}^{(i)}_k)\}} is monotonic, and (ii) the uniqueness of the minimizer (see \eqref{strict_monotonicity}), strict monotonicity of \eqn{\{f(\mbf{z}^{(i)}_k)\}} is ensured in each \ac{SCA} step \cite{scutari2010convex}. \reviewF{Furthermore, by using the fact that \eqn{\{f(\mbf{z}^{(i)}_k)\}} is also bounded, we can show that the objective sequence converges as \eqn{k \to \infty} in \ac{AO} step \eqn{i}, and let \eqn{\mbf{z}_{\lpoint}^{(i)} \triangleq [\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}]} be a stacked vector of the corresponding minimizer of \eqref{con-m} when \eqn{k \to \infty} in \ac{AO} step \eqn{i}.}

@@

\subsection{Stationarity of Limit Points} \label{c-b}
\reviewF{We now discuss the convergence properties of sequence of iterates. For convenience, let us consider a unified superscript \eqn{t} to refer to the index of both \ac{SCA} and \ac{AO} procedures (\textit{i.e.}, index \eqn{t} denotes \ac{SCA} step \eqn{k} and \ac{AO} step \eqn{i}). Then, we denote iterate \eqn{\ma^t} as a vector formed by stacking the minimizer of \eqref{con-m} at iteration \eqn{t} as \eqn{\mat{t} = \mbf{z}^{(i)}_k}, and let \eqn{\{\mat{t}\}} be the sequence formed by collecting the minimizers of \eqref{con-m} from each iteration.

Note that the objective sequence \eqn{\{f(\ma^t)\}} is bounded and nonincreasing (see Appendices \ref{b_obj} and \ref{mcity}). Therefore, by using \cite[Prop. A.3]{bertsekas1999nonlinear}, we can ensure the convergence of \eqn{\{f(\ma^t)\}}. Unfortunately, such a claim cannot be made on the convergence of sequence of iterates \eqn{\{\ma^t\}}. However, due to compactness of the feasible set, the sequence of iterates \eqn{\{\ma^t\} \subset \mc{F}} is bounded. Therefore, the sequence \eqn{\{\mat{t}\}} has at least one limit such that there exists a subsequence of \eqn{\{\ma^t\}} that converges to it, by following \cite[Prop. A.5]{bertsekas1999nonlinear}.

@@

Let us prove the stationarity of \eqn{\bar{\ma}} by contradiction. Assume that \eqn{\bar{\ma}} is not a stationary point. Then there exists some other point \eqn{\ma^\prime \in \{\ma^t\}}, such that \eqn{\nabla f (\bar{\ma})^\tran (\ma^\prime - \bar{\ma}) < 0} and \eqn{f(\bar{\ma}) > f(\ma^\prime)}. Since \eqn{\ma^\prime} is a point in \eqn{\{\ma^t\}}, there exists a subsequence that converges to \eqn{\ma^\prime}, for which \eqn{\ma^\prime} is a limit point. However, by using \eqref{limpoint}, we have \eqn{f(\bar{\ma}) = f(\ma^\prime)} for all limit points of \eqn{\{\ma^t\}}, which is a contradiction to our initial assumption.

Now, by using the strict monotonicity of \eqn{\{f(\ma^{t_j})\}}, it follows that as \eqn{j \to \infty}, \eqn{\ma^{t_j} \to \bar{\ma}} and \eqn{f(\ma^{t_{j}}) - f(\ma^{t_{j+1}}) \to 0}. Moreover, since \eqn{\bar{\ma}} is the solution of \eqref{con-m}, it satisfies \eqref{strict_monotonicity} over convex subset \eqn{\mc{Q}}, which can either be \eqn{\iter{\mc{X}}{k}{i}} or \eqn{\iter{\mc{Y}}{k}{i}} as \eqn{k \to \infty, i \to \infty}. Using the above statements, we can show that \eqn{\bar{\ma}} satisfies the optimality condition  \cite[Prop. 2.1.2]{bertsekas1999nonlinear} as 
\begin{equation} \label{seq_mon1}
\nabla f (\bar{\ma})^\tran (\ma - \bar{\ma}) \geq 0, \; \fall \ma \in \mc{Q} \subset \mc{F} \eqsub.
\end{equation}
Thus, \eqn{\bar{\ma}} is a stationary point, and by using \eqref{limpoint}, we can show that every limit point of \eqn{\{\ma^t\}} is a stationary point of \eqref{con-m}.

@@

Now to prove that \eqn{\bar{\ma}} is also a stationary point of the original problem \eqref{con}, we show the equivalence between the gradients of \eqref{con-m} and \eqref{con} at \eqn{\bar{\ma}}. In order to ensure that \eqn{\bar{\ma}} is a \ac{KKT} point of \eqref{con}, it must satisfy the gradient condition of \eqref{con} as
\begin{equation} \label{kkt_expr}
\textstyle	\nabla \hat{f}(\bar{\ma}) + \mu_0 \big [ \nabla h(\bar{\ma}) - \nabla {g}_0(\bar{\ma}) \big ] + \sum_{i=1}^2 \mu_i \nabla g_i(\bar{\ma}) = 0
\end{equation}
for some Lagrange multipliers \eqn{\mu_i \geq 0} and feasible as \eqn{\bar{\ma} \in \mc{F}}.

Using \eqref{con-sub-set}, we have \eqn{\mc{X}_{k}^{(i)} \subset \mc{F}} and \eqn{\mc{Y}_{k}^{(i)} \subset \mc{F}}, therefore, \eqn{\bar{\ma}} is a feasible point for \eqref{con}. Moreover, the interiors of \eqn{\mc{X}_{k}^{(i)}} and \eqn{\mc{Y}_{k}^{(i)}} are non-empty. Thus, the Slater's constraint qualification holds for \eqref{con-m}. Since \eqn{\bar{\ma}} is the solution for \eqref{con-m} as \eqn{k \to \infty,i \to \infty}, there exist Lagrange multipliers \eqn{\mu_i \geq 0} which satisfy
\begin{equation} \label{kkt_mod_expr}
\textstyle \nabla f(\bar{\ma}) + \mu_0 \big [ \nabla h(\bar{\ma}) - \nabla\hat{g}_0(\bar{\ma};\bar{\ma}) \big ] + \sum_{i=1}^2 \mu_i \nabla g_i(\bar{\ma}) = 0.
\end{equation}

The relation between \eqref{kkt_expr} and \eqref{kkt_mod_expr} is evident by the following facts: (i) The quadratic term in \eqref{mod_obj} \eqn{\|\ma^{t_{j+1}} - \ma^{t_j}\|^2 \to 0}  as \eqn{j \to \infty, \ma^{t_j} \to \bar{\ma}}, since we assume that \eqn{\bar{\ma}} is the limit point of a convergent subsequence \eqn{\{\ma^{t_j}\}}. Therefore, the gradient evaluated at \eqn{\bar{\ma}} satisfies \eqn{\nabla {f}(\bar{\ma}) = \nabla \hat{f}(\bar{\ma})}. (ii) Additionally, by using the continuity of function \eqn{g_o} and \eqref{con-relax}, equivalence between the gradient of \eqref{con-dc} and \eqref{con-dc-m} is obtained as \eqn{\ma^{t_j} \to \bar{\ma}}
\begin{equation} \label{rhs_equiv}
\nabla h(\bar{\ma}) - \nabla \hat{g}_o(\bar{\ma};\bar{\ma}) = \nabla h(\bar{\ma}) - \nabla g_o(\bar{\ma}).
\end{equation}
Now, by applying the relation \eqref{rhs_equiv} and \eqn{\nabla {f}(\bar{\ma}) = \nabla \hat{f}(\bar{\ma})} in \eqref{kkt_mod_expr}, we can show that limit point \eqn{\bar{\ma}} satisfies \eqref{kkt_expr}. Finally, by following \cite[Thm. 2]{scutari_1} and \cite[Prop. 3.2]{amir}, we can show that every limit point of sequence of iterates \eqn{\{\ma^t\}} generated by the iterative method is a stationary point of problem \eqref{con}.}
%using \cite[Thms. 2 and 11]{scutari_1} and \cite[Prop. 3.2]{amir}, we can show that every limit point of sequence of iterates \eqn{\{\ma^t\}} generated by the iterative algorithm is a stationary point of problem \eqref{con}.}

### 2015-11-27 Report/convergence_distributed.tex
submitted

\reviewF{Convergence of the primal decomposition and the \ac{ADMM} follow the same discussions as in Appendix \ref{sec-3.5}, if in each \ac{SCA} step, the distributed schemes converge to the centralized solution. To show that, let us consider subproblem \eqref{eqn-decent-1} in the \eqn{\ith{k}} \ac{SCA} step, solved by distributed method using a regularized objective as in \eqref{mod_obj}. At first, the convergence of the primal decomposition method is discussed by using following properties. (i) The feasible set is non-empty and bounded, therefore, each subproblem satisfies the Slater's constraint qualifications. (ii) Due to strong convexity of the objective \eqref{mod_obj} in subproblem, the minimizer is unique. Therefore, by using the above facts and as \eqn{j \to \infty}, the convergence of the primal decomposition method follows \cite[Prop. 8.2.6]{bertsekas2003convex} by using diminishing step size in each subgradient update.}

>>>>

\reviewF{Convergence of the primal decomposition and the \ac{ADMM} follow the same discussions as in Appendix \ref{sec-3.5}, if in each \ac{SCA} step, the distributed schemes converge to the centralized solution. To show that, let us consider subproblem \eqref{eqn-decent-1} in the \eqn{\ith{k}} \ac{SCA} step, solved by distributed method using a regularized objective as in \eqref{mod_obj}. At first, the convergence of the primal decomposition method is discussed by using the following properties. (i) The feasible set is non-empty and bounded. Therefore, each subproblem satisfies the Slater's constraint qualifications. (ii) Due to the strong convexity of the objective \eqref{mod_obj} in subproblem, the minimizer is unique. Therefore, by using the above facts and as \eqn{j \to \infty}, the convergence of the primal decomposition method follows \cite[Prop. 8.2.6]{bertsekas2003convex} by using a diminishing step size in each subgradient update.}
